Legion: Expressing Locality and Independence with Logical Regions

### 2012-06-30 doc/popl2013/langdef.tex
proof table to fill in

\newcommand{\oton}[1]{{#1}_1,\ldots,{#1}_n}
\newcommand{\otok}[2]{{#2}_1,\ldots,{#2}_{#1}}

@@

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto l, E \\
S' = \text{apply}(S, E, C) \\
v = S'[l]
\end{array}}
{\opsenv \text{read}(e_1) \mapsto v, E ++ [ read(l, v) ]} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto l, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto v, E_2 \\
\end{array}}
{\opsenv \text{write}(e_1, e_2) \mapsto true, E_1 ++ E_2 ++ [ write(l, v) ]} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto l, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto v, E_2 \\
\end{array}}
{\opsenv \text{reduce}(id, e_1, e_2) \mapsto true, E_1 ++ E_2 ++ [ reduce_{id}(l, v) ]} \\

@@

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto K, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto l, E_2 \\
S'' = \text{apply}(S', E_2, C) \\
\opsenvs{S''} e_3 \mapsto v, E_3 \\
K' = \{ (l,v) \} \cup \{ (l_i,v_i) : (l_i,v_i) \in K \wedge l \not= l_i \}
\end{array}}
{\opsenv \text{color}(e_1, e_2, e_3) \mapsto K', E_1 ++ E_2 ++ E_3} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto v_1, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto v_2, E_2 \\
v' = v_1 + v_2
\end{array}}
{\opsenv e_1 + e_2 \mapsto v', E_1 ++ E_2} \hspace{1cm}

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto v_1, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto v_2, E_2 \\
v' = \begin{cases}
true, & \text{if $v_1 < v_2$}. \\
false, & \text{otherwise}.
\end{cases}
\end{array}}
{\opsenv e_1 < e_2 \mapsto v', E_1 ++ E_2} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto v_1, E_1 \\
L' = L[v_1/id] \\
S' = \text{apply}(S, E_1, C) \\
\opsenvls{L'}{S'} e_2 \mapsto v_2, E_2
\end{array}}
{\opsenv \text{let }id : T = e_1\text{ in }e_2 \mapsto v_2, E_1 ++ E_2} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto true, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvls{L'}{S'} e_2 \mapsto v_2, E_2
\end{array}}
{\opsenv \text{if }e_1\text{ then }e_2\text{ else }e_3 \mapsto v_2, E_1 ++ E_2} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto false, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvls{L'}{S'} e_3 \mapsto v_3, E_3
\end{array}}
{\opsenv \text{if }e_1\text{ then }e_2\text{ else }e_3 \mapsto v_3, E_1 ++ E_3} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto v_1, E_1 \\
S_1 = \text{apply}(S, E_1, C) \\
\opsenv e_2 \mapsto v_2, E_2 \\
\ldots \\
S_n = \text{apply}(S_{n-1}, E_n, C) \\
task id[\otok{k}{r'}](f_1 : T_1, \ldots, f_n : T_n) : T_r, E = e_{n+1} \\
M' = \{ (r'_1, M(r_1)), \ldots (r'_k, M(r_k)) \} \\
L' = \{ (f_1, v_1), \ldots, (f_n, v_n) \} \\
\opsenvmls{M'}{L'}{S_n} e_{n+1} \mapsto v_{n+1}, E_{n+1}
\end{array}}
{\opsenv id[\otok{k}{r}](\oton{e}) \mapsto v_{n+1}, E_1 ++ \ldots ++ E_{n+1}} \\

\finfrule{
\begin{array}{l}
\opsenv e_1 \mapsto K, E_1 \\
\rho_i = \{ l : (l, i) \in K \} \\
M' = M[\rho_1/r_1, \ldots, \rho_k/r_k] \\
S' = \text{apply}(S, E_1, C) \\
\opsenvms{M'}{S'} e_2 \mapsto v, E_2
\end{array}}
{\opsenv \text{partition}\ r_p\text{ using }e_1\text{ as }\otok{k}{r}\text{ in }e_2 \mapsto v, E_1 ++ E_2} \\

@@

\finfrule{
\begin{array}{l}
\opsenv e_1 \mapsto \langle \langle \otok{k}{\rho} , v_1 \rangle \rangle, E_1 \\
M' = M[\rho_1/r_1, \ldots, \rho_k/r_k] \\
L' = L[v_1/id] \\
S' = \text{apply}(S, E_1, C) \\
\opsenvmls{M'}{L'}{S'} e_2 \mapsto v_2, E_2
\end{array}}
{\opsenv \text{unpack}\ e_1\ \text{as}\ id : T_1[\otok{k}{r}] \text{in}\ e_2 \mapsto v_2, E_1 ++ E_2 } \\

@@

If
\begin{enumerate}
\item $\typeenv e : T$
\item $\opsenv e \mapsto v, E$
\end{enumerate}
then for all effects $\epsilon$ in $E$,
\begin{enumerate}
\item if $\epsilon = read(l, v)$, then for some $r$, $reads(r) \in \Phi \wedge l \in M(r)$
\item if $\epsilon = write(l, v)$, then for some $r$, $writes(r) \in \Phi \wedge l \in M(r)$
\item if $\epsilon = reduce(id, l, v)$, then for some $r$, $reduces(id,r) \in \Phi \wedge l \in M(r)$
\end{enumerate}

@@

\finfrule
{\begin{array}{l}
\typeenv e : T \\
\opsenv e \mapsto v, E \\
M \sim \Omega \hspace{1cm}
L \sim_H \Gamma \hspace{1cm}
S \sim H
\end{array}}
{
v \sim_H M \llbracket T \rrbracket \hspace{1cm}
E \sim_H \Phi
}

@@

\finfrule
{\begin{array}{l}
E_1 \sim_H \Phi \hspace{1cm}
E_2 \sim_H \Phi
\end{array}}
{ E_1 ++ E_2 \sim_H \Phi }

>>>>

\newcommand{\oton}[1]{{#1}_1,\ldots,{#1}_n}
\newcommand{\otok}[2]{{#2}_1,\ldots,{#2}_{#1}}
\newcommand{\dplus}{\text{++}}

@@

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto l, E \\
S' = \text{apply}(S, E, C) \\
v = S'[l]
\end{array}}
{\opsenv \text{read}(e_1) \mapsto v, E \dplus [ read(l, v) ]} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto l, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto v, E_2 \\
\end{array}}
{\opsenv \text{write}(e_1, e_2) \mapsto true, E_1 \dplus E_2 \dplus [ write(l, v) ]} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto l, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto v, E_2 \\
\end{array}}
{\opsenv \text{reduce}(id, e_1, e_2) \mapsto true, E_1 \dplus E_2 \dplus [ reduce_{id}(l, v) ]} \\

@@

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto K, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto l, E_2 \\
S'' = \text{apply}(S', E_2, C) \\
\opsenvs{S''} e_3 \mapsto v, E_3 \\
K' = \{ (l,v) \} \cup \{ (l_i,v_i) : (l_i,v_i) \in K \wedge l \not= l_i \}
\end{array}}
{\opsenv \text{color}(e_1, e_2, e_3) \mapsto K', E_1 \dplus E_2 \dplus E_3} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto v_1, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto v_2, E_2 \\
v' = v_1 + v_2
\end{array}}
{\opsenv e_1 + e_2 \mapsto v', E_1 \dplus E_2} \hspace{1cm}

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto v_1, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvs{S'} e_2 \mapsto v_2, E_2 \\
v' = \begin{cases}
true, & \text{if $v_1 < v_2$}. \\
false, & \text{otherwise}.
\end{cases}
\end{array}}
{\opsenv e_1 < e_2 \mapsto v', E_1 \dplus E_2} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto v_1, E_1 \\
L' = L[v_1/id] \\
S' = \text{apply}(S, E_1, C) \\
\opsenvls{L'}{S'} e_2 \mapsto v_2, E_2
\end{array}}
{\opsenv \text{let }id : T = e_1\text{ in }e_2 \mapsto v_2, E_1 \dplus E_2} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto true, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvls{L'}{S'} e_2 \mapsto v_2, E_2
\end{array}}
{\opsenv \text{if }e_1\text{ then }e_2\text{ else }e_3 \mapsto v_2, E_1 \dplus E_2} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto false, E_1 \\
S' = \text{apply}(S, E_1, C) \\
\opsenvls{L'}{S'} e_3 \mapsto v_3, E_3
\end{array}}
{\opsenv \text{if }e_1\text{ then }e_2\text{ else }e_3 \mapsto v_3, E_1 \dplus E_3} \\

\finfrule
{\begin{array}{l}
\opsenv e_1 \mapsto v_1, E_1 \\
S_1 = \text{apply}(S, E_1, C) \\
\opsenv e_2 \mapsto v_2, E_2 \\
\ldots \\
S_n = \text{apply}(S_{n-1}, E_n, C) \\
task id[\otok{k}{r'}](f_1 : T_1, \ldots, f_n : T_n) : T_r, E = e_{n+1} \\
M' = \{ (r'_1, M(r_1)), \ldots (r'_k, M(r_k)) \} \\
L' = \{ (f_1, v_1), \ldots, (f_n, v_n) \} \\
\opsenvmls{M'}{L'}{S_n} e_{n+1} \mapsto v_{n+1}, E_{n+1}
\end{array}}
{\opsenv id[\otok{k}{r}](\oton{e}) \mapsto v_{n+1}, E_1 \dplus \ldots \dplus E_{n+1}} \\

\finfrule{
\begin{array}{l}
\opsenv e_1 \mapsto K, E_1 \\
\rho_i = \{ l : (l, i) \in K \} \\
M' = M[\rho_1/r_1, \ldots, \rho_k/r_k] \\
S' = \text{apply}(S, E_1, C) \\
\opsenvms{M'}{S'} e_2 \mapsto v, E_2
\end{array}}
{\opsenv \text{partition}\ r_p\text{ using }e_1\text{ as }\otok{k}{r}\text{ in }e_2 \mapsto v, E_1 \dplus E_2} \\

@@

\finfrule{
\begin{array}{l}
\opsenv e_1 \mapsto \langle \langle \otok{k}{\rho} , v_1 \rangle \rangle, E_1 \\
M' = M[\rho_1/r_1, \ldots, \rho_k/r_k] \\
L' = L[v_1/id] \\
S' = \text{apply}(S, E_1, C) \\
\opsenvmls{M'}{L'}{S'} e_2 \mapsto v_2, E_2
\end{array}}
{\opsenv \text{unpack}\ e_1\ \text{as}\ id : T_1[\otok{k}{r}] \text{in}\ e_2 \mapsto v_2, E_1 \dplus E_2 } \\

@@

If
\begin{enumerate}
\item $\typeenv e : T$
\item $\opsenv e \mapsto v, E$
\end{enumerate}
we would like to prove that all of the dynamic effects described by $E$ are
included in the static privileges $\Phi$.  A judgement $E : \Phi$ means that
for all effects $\epsilon$ in $E$,
\begin{enumerate}
\item if $\epsilon = read(l, v)$, then for some $r$, $reads(r) \in \Phi \wedge l \in M(r)$
\item if $\epsilon = write(l, v)$, then for some $r$, $writes(r) \in \Phi \wedge l \in M(r)$
\item if $\epsilon = reduce(id, l, v)$, then for some $r$, $reduces(id,r) \in \Phi \wedge l \in M(r)$
\end{enumerate}

@@

\finfrule
{\begin{array}{l}
\typeenv e : T \\
\opsenv e \mapsto v, E \\
M \sim \Omega \hspace{1cm}
L \sim_H \Gamma \hspace{1cm}
S \sim H
\end{array}}
{
v \sim_H M \llbracket T \rrbracket \hspace{1cm}
E \sim H \hspace{1cm}
E : \Phi
}

@@

\finfrule
{\begin{array}{l}
E_1 : \Phi \hspace{1cm}
E_2 : \Phi
\end{array}}
{ E_1 \dplus E_2 : \Phi } \\

\framebox{$M \sim \Omega \Leftrightarrow M \sim \Omega^*$} \\

\framebox{$E : \Phi \Leftrightarrow E : \Phi^*$}

\begin{table*}
\centering
{\small
\begin{tabular}{l|p{5cm}|p{5cm}|p{5cm}}
{\bf Rule} & 
\multicolumn{1}{|c|}{$\mathbf{v \sim_H M \llbracket T \rrbracket}$} &
\multicolumn{1}{|c|}{$\mathbf{E \sim H}$} &
\multicolumn{1}{|c|}{$\mathbf{E : \Phi}$} \\
\hline
BoolConst & & & \\
IntConst & & & \\
TupleBuild & & & \\
TupleField & & & \\
LocalVar & & & \\
NullPtr & & & \\
NewPtr & & & \\
IsNull & & & \\
UpRegion & & & \\
DownRegion & & & \\
Read & & & \\
Write & & & \\
Reduce & & & \\
Newcolor & & & \\
Color & & & \\
IntMath & & & \\
IntCmp & & & \\
Let & & & \\
IfElse & & & \\
TaskCall & & & \\
Partition & & & \\
Pack & & & \\
Unpack & & &
\end{tabular}}
\caption{Proof pieces}
\end{table*}
